TSVD_MSSA

### 2025-03-22 Code/R/Research/TSVD_MSSA.Rmd
Further tsvd research

# Using TSVD for MSSA
## Setup
```{r}
N <- 71
ones <- rep(1, N)
## 1
# A <- ones %o% seq(25, 35, 2.5)
# w <- rep(1 / 12, 5)
# phi <- ones %o% rep(0, 5)
# save_file_name <- "same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

## 2
A <- ones %o% c(30, 20, 25, 32)
w <- c(1 / 12, 1 / 8, 1/12, 1/8)
phi <- ones %o% c(0, pi / 2, 2 * pi / 2, 3 * pi / 2)
save_file_name <- "diff_freq_diff_phase"
groups_mssa <- list(1:4)
groups3 <- list(1:2)
groups_tsvd <- list(1:4)

@@

max.r <- max(sapply(groups_mssa, max))
max.rtsvd <- max(sapply(groups_tsvd, max))

@@

>>>>

# Using TSVD for MSSA
## Setup
```{r}
N <- 71
ones <- rep(1, N)

## 0
A <- ones %o% rep(30, 5)
w <- rep(1 / 12, 5)
phi <- ones %o% rep(0, 5)
save_file_name <- "same_all"
groups_mssa <- list(1:2)
groups3 <- list(1)
groups_tsvd <- list(1:2)

## 1
# A <- ones %o% seq(25, 35, 2.5)
# w <- rep(1 / 12, 5)
# phi <- ones %o% rep(0, 5)
# save_file_name <- "same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_tsvd <- list(1:2)

## 2
# A <- ones %o% c(30, 20, 25, 32)
# w <- c(1 / 12, 1 / 8, 1/12, 1/8)
# phi <- ones %o% c(0, pi / 2, 2 * pi / 2, 3 * pi / 2)
# save_file_name <- "diff_freq_diff_phase"
# groups_mssa <- list(1:4)
# groups3 <- list(1:2)
# groups_tsvd <- list(1:4)

@@

max.r <- max(sapply(groups_mssa, max), 2)
max.rtsvd <- max(sapply(groups_tsvd, max), 2)

@@

plan(multisession)
# plan("default")
